---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# GoodReads

<!-- badges: start -->
<!-- badges: end -->

The `GoodReads` package lets you webscrape a book lists information from [GoodReads Listopia](https://www.goodreads.com/list/tag/best). The package alo allows you to plot the cover of a book from its given rank.


## Installation

You can install the development version of the GoodReads package from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("aoluyadi/BookPackage")
```

## Usage

Using a url from Goodread’s Listopia of Best Books Lists, the package webscrapes information for the first 100 books. 

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(GoodReads)

Best_Books_Everdf <- book_details("https://www.goodreads.com/list/show/1.Best_Books_Ever")

Hunger_Games <- book_cover(Best_Books_Everdf, 1)

```
