---
title: “Using the GoodReads package”
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the GoodReads package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Browsing GoodReads books 

The main function of the GoodReads package is to let you browse books from the GoodReads website. This function uses the best books ever category as an example data frame and  provides you with links to web scrape and create more comprehensible data frames within r  to browse numerous book categories from the listopia from good reads. 
Here’s an example of how to accomplish this. First, load the `GoodReads` package.

```{r setup}
library(GoodReads)
```

Then, use the `book_details()` to retrieve information about a particular book and their ranking within a specific category in good reads. Here lets retrieve the Best Young Adult Books.

```{r}
Best_YA_Booksdf <- GoodReads::book_details("https://www.goodreads.com/list/show/43.Best_Young_Adult_Books")
```

The object that is returned is book info date set: rank, book names, author, series, average rating, total rating and cover id. This provides you with the rank information that is then used directly as an argument for book_cover. `book_cover()` allows you to view the book cover images. Here is the code to load the cover for Harry Potter and Sorcerer’s Stone (Harry Potter, #1). 

```{r}
book_cover(Best_YA_Booksdf, 1)
```

## GoodReads Best Books Ever Data 
The GoodReads package also comes with a built-in data set describing the 100 best books ever published on the GoodReads website. This can be viewed by loading:

```{r}
GoodReads::bestbooksever_df
```
